### 2018-01-05 includes/abstract.tex
Adjusting the abstract.

    Many SMT solvers that support the theory of strings have been developed over the past decade, and several have matured to the point of being performant and practically useful. Moreover a standard input language, SMT-LIB, has been developed, and many mature solvers support it. In this paper we present StringFuzz, a fuzzer and problem generator for string solvers. With it we analyse four mature string solvers: Z3str3, Norn, CVC4, and ABC. We use it to craft inputs that elicit poor performance in Z3str3 and CVC4, and present algorithmic improvements to mitigate it. Finally, we present several minor bugs in Z3str3 that were exposed by StringFuzz.

>>>>

    Many SMT solvers that support the theory of strings have been developed over the past decade, and several have matured to the point of being performant and practically useful. Moreover a standard input language, SMT-LIB, has been developed, and many mature solvers support it. In this paper we present StringFuzz: a fuzzer and SMT-LIB problem generator for string solvers. With it we analyse four mature string solvers: Z3str3, Norn, CVC4, and ABC. We use it to craft inputs that elicit poor performance in Z3str3 and CVC4, and provide algorithmic analyses of the causes of the performance degradations. Finally, we present several minor bugs in Z3str3 that were exposed by StringFuzz, to justify its further use by other solver authors to likewise improve their solvers.
